---
output: rmarkdown::github_document
---
```{r}
pkgdown::build_site()
```

```{r, comment=""}
library(knitr)
knit_rd("StatTools")

```

**Regby**: Is a regby function that summarizes a stratified analysis results of
 regression models. <br>
DESCRIPTION
:<br>  
This function helps to extract the important
 regression summaries such as coefficients, confidence intervals, and P-value
 in stratified analysis. Currently, this package is implemented for the most
 commonly used regression analysis such as linear regression, logistic
 regression, Poisson regression, proportional odds logistic regression (using
 polr in MASS package), multinomial regression (using multinom nnet package),
 Cox proportional hazard regression (using coxph in survival package), and
 linear mixed models (lmer in lme4 package). For poisson regression, use the 
 glm model with fam=poisson and EXP=TRUE to get incidence rate ratio. 
 
 
 
**Usage** <br>
regby( <br>
  datain,<br>
  byVar,<br>
  frmlYX,<br>
  fam = NULL,<br>
  Pred,<br>
  Factor = FALSE,<br>
  Intercept = FALSE,<br>
  EXP = TRUE,<br>
  Model,<br>
  col.names = TRUE,<br>
  colname,<br>
  ...<br>
)<br><br>
****Arguments****<br>
**datain**	<br>
Is the input dataset

**byVar**	<br>
Is the stratifying categorical variable. <br>

**frmlYX**	<br>
The model formula.

**fam**	<br>
Distribution family for the output variable. Examples are binomial, poisson, etc.<br>

**Pred**	<br>
Is a list containing the predictor variables names in the order they appear in the model formula.For example, if Z is a factor predictor variable and has a, b, c, and d levels, unless otherwise the reference is re-leveled, the coefficients will be output in alphabetical order with the first level being the reference level. Thus, include in the "Pred" list the levels for which the coefficients are output as Pred=c("Other-predictors", "Zb", "Zc", "Zd") in the order they appear in the model formula.<br>

**Factor**<br>	
Whether there are categorical predictors in the model. It defaults to FALSE.<br>

**Intercept**<br>	
Whether you want the intercept output or not. It defaults to FALSE. If you want the intercept, include Intercept as the first list Pred name lists.<br>

**EXP**	<br>
Whether you want the exponentiation of the estimate and CIs. EXP defaults to TRUE.<br>

**Model**	<br>
The regression function name such as lm, glm, coxph.<br>

**col.names**	<br>
Whether the user wants to rename column names. Default=TRUE.<br>

**colname**	<br>
lists of the column header names.<br>

**...**	
Expandable.<br>
 
 
 **EXAMPLES**
 
 
## Logistic regression analysis with a continuous and Categorical predictors, and intercept not requested 
 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}

library(StatTools)
set.seed(123896) 
requireNamespace("htmlTable",quietly=TRUE)
x=rnorm(100) 
z=sample(letters[1:4], 100, TRUE) 
R<-c('B', 'W') 
Cat<-sample(R, 100, TRUE) 
y=rbinom(100, 1, 0.5) 
data1<-data.frame(x=x,z=z, Cat=Cat, y=y ) 


#If Factor==TRUE include the level labels of the predictor as separate names.
 regby(datain=data1, byVar='Cat',
 frmlYX=formula(y~x+z), 
 fam=binomial, 
 Model="glm", 
 Pred=c("Intercept",
  "X","Zb",
 "Zc", "Zd"),  colname=c("Strata", "Variable", "OR(95%CIs)", "P-value" ),
 Factor=TRUE, Intercept=FALSE, EXP=TRUE)
```
<br><br><br><br><br>

## Multiple Linear regression analysis with a continuous and Categorical predictors, and intercept included
 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}

regby(datain=data1, byVar='Cat', frmlYX=formula(y~x+z), fam=guassian,
Model="lm",Pred=c("Intercept", "X","Zb", "Zc", "Zd"), 
colname=c("Strata", "Variable", "Beta (95%CIs)", "P-value" ), 
Factor=TRUE, Intercept=TRUE, EXP=FALSE)
```
<br><br><br><br><br>


```{r}
regby(datain=mtcars, byVar='cyl', frmlYX=formula(disp~factor(gear)+factor(am)+vs), fam=guassian,
      Model="lm",Pred=NULL, 
      colname=c("Strata", "Variable", "Beta (95%CIs)", "P-value" ), 
      Factor=TRUE, Intercept=TRUE, EXP=FALSE)
```
<br><br><br><br><br>

## Cox proportional hazard regression analysis with a continuous predictor

 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}

set.seed(1243567)
t<-rnorm(100, 15, 3)
y<-rbinom(100, 1, 0.5)
Cat<-sample(c("M", "F"), 100, TRUE)
x<-rnorm(100, 5, 2)
z<-rpois(100,1)
z<-factor(z)
data2<-data.frame(t=t, x=x, Cat=Cat, y=y,z)
require('survival')

regby(datain=data2, byVar='Cat', frmlYX=formula(Surv(t,y)~x),
Model="coxph", Pred=c( "X"),  colname=c("Strata", "Variable", 
"HR (95%CIs)", "P-value" ), Factor=TRUE, Intercept=FALSE)
```
 <br><br><br><br><br>

## Proportional Odds Ordered Logistic Regression
 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}

 x<-rnorm(50)
 z<-sample(c(letters[1:5]), 50, TRUE)
 Cat<-sample(R, 50, TRUE)
 y<-rbinom(50, 1, 0.5)
 data3<-data.frame(x=x, z=z, Cat=Cat, y=y)

 regby(datain=data3, byVar='Cat', frmlYX=formula(z~x), Model="polr", 
  colname=c("Strata", "Variable", "Beta (95%CIs)", "P-value", 
  "Cum_Prob", "OR" ), Factor=TRUE, Intercept=FALSE, col.names = TRUE)
```
<br><br><br><br><br>

## Multinomial Logistic Regression
 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}

 regby(datain=data3, byVar='Cat',  frmlYX=(z~x), Model = "multinom",  
 colname=c("Strata", "Variable", "OR (95%CIs)", "P-value" ), Factor=TRUE, 
 Intercept=FALSE)
```
<br><br><br><br><br>

## Linear Mixed Effect Models
 
```{r, echo=TRUE, warning=FALSE, message=FALSE, comment=""}
 regby(datain=data3, byVar='Cat',  frmlYX=(x~y+(1|z)), Model = "lmer", 
 col.names = FALSE)
```
<br><br><br><br><br>


